---
title: "Demographics"
author: "Dennis Wollersheim and Scott Groton"
date: "2020-09-10"
output:
  workflowr::wflow_html:
    toc: false
---


```{r include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=8)
source('_drake.R')


```

# Results for data excluding cohorts where n<=3

```{r graph_raw, include=FALSE}

loadd( df_in_long_filtered )


```


## Total number of children across the whole sample

```{r tables}

 df_in_long_filtered  %>%
   distinct(id) %>%
   count() %>%
   gt()

```

## Median and SD age at start (inc Ms and SDs)


```{r tables2}

df_in_long_filtered  %>%
  select(id, cohort_age) %>%
  group_by(id) %>%
  filter( cohort_age == min( cohort_age)) %>%
  distinct() %>%
  ungroup() %>%
  summarise( mean_age = mean(cohort_age), sd_age = sd(cohort_age),.groups='drop') %>%
  gt()

```


## Number of children in each cohort at baseline, age (inc Ms and SDs).

```{r tables3}

df_in_long_filtered  %>%
  select(cohort, id, cohort_age) %>%
  group_by(id) %>%
  filter( cohort_age == min( cohort_age)) %>%
  distinct() %>%
  group_by(cohort) %>%
  summarise( mean_age = mean(cohort_age), sd_age = sd(cohort_age), number_in_cohort=n(), .groups='drop') %>%
  gt()



```

