---
title: "Demographics"
author: "Dennis Wollersheim and Scott Groton"
date: "2020-09-10"
output:
  workflowr::wflow_html:
    toc: false
---


```{r include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=8)
source('_drake.R')


```

# Results for data excluding cohorts where n<=3

```{r graph_raw, include=FALSE}

loadd( df_in_long_filtered )
loadd( df_in)


```


## Total number of children across the whole sample

```{r tables}

 df_in_long_filtered  %>%
   distinct(id) %>%
   count() %>%
   gt()

```

## Median and SD age at start (inc Ms and SDs)


```{r tables2}

df_in_long_filtered  %>%
  select(id, cohort_age) %>%
  group_by(id) %>%
  filter( cohort_age == min( cohort_age)) %>%
  distinct() %>%
  ungroup() %>%
  summarise( mean_age = mean(cohort_age), sd_age = sd(cohort_age),.groups='drop') %>%
  gt()

```


## Number of children in each cohort at baseline, age (inc Ms and SDs).

```{r tables3}

df_in_long_filtered  %>%
  select(cohort, id, cohort_age) %>%
  group_by(id) %>%
  filter( cohort_age == min( cohort_age)) %>%
  distinct() %>%
  group_by(cohort) %>%
  summarise( mean_age = mean(cohort_age), sd_age = sd(cohort_age), number_in_cohort=n(), .groups='drop') %>%
  gt()



```


## Number of children in each age group at baseline, age (inc Ms and SDs).
where age is age_corrected/12 and age_group is round(age), e.g.
6 years old group includes ages 5.5-6.5


```{r tables_ages}

df_in %>%
  mutate( id = str_trim(id)) %>%
  inner_join( df_in_long_filtered  %>% distinct( id) ) %>%
  select(age_corrected) %>%
  mutate( age = age_corrected / 12, age_group=round(age)) %>%
  group_by( age_group) %>%
  summarise( mean_age = mean(age), sd_age= sd(age), n=n(), .groups='drop') %>%
  gt()

df_in %>%
  mutate( id = str_trim(id)) %>%
  inner_join( df_in_long_filtered  %>% distinct( id) ) %>%
  select(age_corrected, sex) %>%
  mutate( age = age_corrected / 12, age_group=round(age)) %>%
  group_by( age_group, sex) %>%
  summarise( mean_age = mean(age), sd_age= sd(age), n = n(),  .groups='drop') %>%
  pivot_wider(id_cols=age_group,
              values_from=c(mean_age, sd_age, n),
              names_from=sex) %>%
  gt()


```


## Number of children in each age group at baseline, age (inc Ms and SDs) (including ALL participants unfiltered)


```{r tables_ages_unfiltered}

df_in %>%
  mutate( id = str_trim(id)) %>%
  select(age_corrected) %>%
  mutate( age = age_corrected / 12, age_group=round(age)) %>%
  group_by( age_group) %>%
  summarise( mean_age = mean(age), sd_age= sd(age), n=n(), .groups='drop') %>%
  gt()

df_in %>%
  mutate( id = str_trim(id)) %>%
  select(age_corrected, sex) %>%
  mutate( age = age_corrected / 12, age_group=round(age)) %>%
  group_by( age_group, sex) %>%
  summarise( mean_age = mean(age), sd_age= sd(age), n = n(),  .groups='drop') %>%
  pivot_wider(id_cols=age_group,
              values_from=c(mean_age, sd_age, n),
              names_from=sex) %>%
  gt()


```

