---
title: "Initial Analysis"
author: "Dennis Wollersheim"
date: "15.04.2020"
output:
  html_document:
    df_print: paged
  pdf_document:
    highlight: zenburn
linkcolor: cyan
citecolor: grey
---

\tableofcontents

```{r include=FALSE}

source('_drake.R')


```

# Raw results, no filtering

```{r graph_raw, results='asis'}

loadd(df_one_names)
loadd( df_in_long )
loadd( df_in_long_filtered )

df_in_long %>%
  distinct( type ) %>%
  mutate( variable = paste0(prefix, type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(make_one_graph_set, df_in_long) %>%
  { . } -> dev_null

```

# Raw BIC values

```{r}

readd(df_model) %>%
  gt() %>%
  data_color(
             columns = 2:8,
             colors = scales::col_numeric(
                                          palette = paletteer::paletteer_d(
                                                                           palette = "ggsci::red_material"
                                                                           ) %>% as.character(),
                                          domain = NULL
                                          ),
             alpha = 0.8
  )

```


# Results with all cohorts / periods removed that have N < 3

```{r graph_filtered, results='asis'}

df_in_long_filtered  %>%
  distinct( type ) %>%
  mutate( variable = paste0(prefix, type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(make_one_graph_set,  df_in_long_filtered) %>%
  { . } -> dev_null

```

# Filtered BIC values

```{r}
readd(df_model_filtered) %>% 
  gt() %>%
  data_color(
             columns = 2:8,
             colors = scales::col_numeric(
                                          palette = paletteer::paletteer_d(
                                                                           palette = "ggsci::red_material"
                                                                           ) %>% as.character(),
                                          domain = NULL
                                          ),
             alpha = 0.8
  )
```

# Reproducibility

```{r}
## datetime
Sys.time()

## repository
git2r::repository()

## session info
sessionInfo()
```






