---
title: "Initial Analysis"
author: "Dennis Wollersheim"
date: "15.04.2020"
output:
  html_document:
    df_print: paged
  pdf_document:
    highlight: zenburn
linkcolor: cyan
citecolor: grey
---

\tableofcontents

```{r include=FALSE}

source('_drake.R')


```

# Raw results, no filtering

```{r graph_raw, results='asis'}

loadd(df_one_names)

loadd(df_age_label)

loadd( df_in_long )
loadd( df_in_long_filtered )
loadd( df_in_long_filtered_twice )

loadd( df_mlm_model )
loadd( df_mlm_model_filtered )
loadd( df_mlm_model_filtered_twice )

df_in_long %>%
  distinct( type ) %>%
  mutate( variable = paste0(prefix, type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(make_one_graph_set, df_in_long) %>%
  { . } -> dev_null

```

## Raw BIC values

```{r}

df_mlm_model %>%
  distinct( target_type ) %>%
  mutate( variable = paste0(prefix, target_type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(display_one_model_set, df_mlm_model) %>%
  { . } -> dev_null

```


# Results with all cohorts / periods removed that have N < 3

```{r graph_filtered, results='asis'}

df_in_long_filtered  %>%
  distinct( type ) %>%
  mutate( variable = paste0(prefix, type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(make_one_graph_set,  df_in_long_filtered) %>%
  { . } -> dev_null

```

## Filtered BIC values

```{r}

df_mlm_model_filtered %>%
  distinct( target_type ) %>%
  mutate( variable = paste0(prefix, target_type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(display_one_model_set, df_mlm_model_filtered) %>%
  { . } -> dev_null

```




# Results with all cohorts / periods removed that have N < 3, and outliers >3 standard deviations removed

```{r graph_filtered_twice, results='asis'}

df_in_long_filtered_twice  %>%
  distinct( type ) %>%
  mutate( variable = paste0(prefix, type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(make_one_graph_set,  df_in_long_filtered_twice) %>%
  { . } -> dev_null

```
## Double filtered BIC values

```{r}

df_mlm_model_filtered_twice %>%
  distinct( target_type ) %>%
  mutate( variable = paste0(prefix, target_type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(display_one_model_set, df_mlm_model_filtered_twice) %>%
  { . } -> dev_null

```

## Outlier summary

```{r}

readd(df_outliers) %>%
  mutate( variable = paste0(prefix, type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  count(label) %>%
  mutate( label = str_replace_all(label, 'Groton Maze: | Total','')) %>%
  gt()  %>%
  tab_header(
             title = "Outlier Exclusion Summary",
             subtitle = "Number of outliers excluded per variable category"
             ) %>%
  cols_label( label='Variable',n='Number Excluded')


```

# Reproducibility

```{r}
## datetime
Sys.time()

## repository
git2r::repository()

## session info
sessionInfo()
```






