---
title:           Initial Analysis
author:          Dennis Wollersheim
date:            15.04.2020
linkcolor:       cyan
citecolor:       grey
output:
  pdf_document:
    highlight:   zenburn
---

\tableofcontents

```{r include=FALSE}

source('_drake.R')


```

# Raw results, no filtering

```{r graph_raw, results='asis'}

loadd(df_one_names)
loadd(df_in_long)

df_in_long %>%
  distinct( type ) %>%
  mutate( variable = paste0(prefix, type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(make_one_graph_set, df_in_long) %>%
  { . } -> dev_null

```

# Raw BIC values

```{r}
readd(df_model) %>% gt()
```


# Results with all cohorts / periods removed that have N < 3

```{r graph_filtered, results='asis'}

df_in_long %>%
  filter( type == 'mps') %>%
  group_by( cohort,period ) %>%
  filter( n() <3 )  %>%
  distinct ( cohort, period) %>%
  ungroup() %>%
  { . } -> df_tofilter

df_in_long %>%
  distinct( type ) %>%
  mutate( variable = paste0(prefix, type) ) %>%
  inner_join( df_one_names, by='variable' ) %>%
  by_row(make_one_graph_set, anti_join( df_in_long, df_tofilter) ) %>%
  { . } -> dev_null

```

# Reproducibility

```{r}
## datetime
Sys.time()

## repository
git2r::repository()

## session info
sessionInfo()
```






